The Fates of Merging Supermassive Black Holes and a Proposal for a New Class of X-Ray Sources

### 2020-03-11 paper.tex
Rewrote Black Hole Accretion and Luminosity Section ($4.2.3)

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages

@@

\begin{abstract}
We perform follow-up N-body simulations on some of the most massive galaxies extracted from a cosmological simulation of hierarchical structure formation with total masses in the range $10^{12} M_{\sun} < M < 3\times 10^{13} M_{\sun}$ from $4\geq z \geq 0$.  After galactic mergers, we track the dynamical evolution of the infalling black holes (BHs) around their host's central BHs.  From 11 different simulations, we find that, of the 86 infalling BHs with masses > $10^4 M_{\sun}$, 36 merge with their host's central BH, 13 are ejected from their host galaxy, and 37 are still orbiting at $z=0$.  Across all galaxies, 33 BHs are kicked to a higher orbit after close interactions with the central BH binary or multiple, after which only one of them merged with their hosts.  These orbiting BHs should be detectable by their anomalous (not LMXRB) spectra.  The X-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{28}-10^{43}$ $\mathrm{erg}~\mathrm{s}^{-1}$, with a currently undetectable median value of $10^{33}$ $\mathrm{erg}~\mathrm{s}^{-1}$.  However, the most luminous $\sim$5\% should be detectable by existing X-ray facilities.
\end{abstract}

@@

\subsection{Overview of simulation}
The computational challenge of this investigation is a wide range of time-scales. Galactic evolution and galactic orbits take hundreds of millions to billions of years, while orbital times of BH binaries may require times steps of years for accurate integration. We overcome this challenge by simplifying the model where possible, and by focussing on the main drivers of BH dynamics: the galactic background potential, dynamical friction, and strong BH-BH encounters.

@@

For the numerical simulations presented here, we used a modified version of the algorithmic chain integrator \textsc{AR-Chain} developed by \citet{2006MNRAS.372..219M}. It uses algorithmic chain regularization for high-precision integration of few-body dynamics, and is capable of handling velocity-dependent forces efficiently. It includes relativistic post-Newtonian terms up to order PN2.5 \citep{2008AJ....135.2398M}.

@@

\citet{2012MNRAS.425..641L}, using \citet{2011ApJ...741...99C}'s work as a basis, created galactic merger trees that compared the properties of in-situ and accreted stellar mass of galaxies at redshift snapshots between $4 \geq z \geq 0$.

@@

\subsubsection{Stellar Mass Adjustment}
As we will explain further in Section \ref{Galaxy background potential}, in our simulations orbiting black holes are inserted into the host galaxy at the effective radius, $R_e$, which is partially dependent on stellar mass, $M_*$ (see Eqn. \ref{re}).  For every doubling of the stellar mass, $R_e$ increases by a factor of 1.66.  Additionally, the velocity dispersion at the effective radius, $\sigma(R_e)$, which is used to set the parameter $r_h$ (see Eqn. \ref{jerry}) of our dark matter profile, is also dependent on $M_*$.  In this case, a doubling of $M_*$ would increase $\sigma(R_e)$ by a factor of 1.15.  These variations have direct effects on the ability of the orbiting black holes to merge with the central black hole, and thus can affect our merger statistics and resulting characteristic strain calculations, and therefore it is important to estimate our stellar masses with reasonable accuracy.

@@

\subsection{Simulation Physics}
In this section, we describe the underlying physics of our simulations, including choice of galaxy background potential, BH diffusion through the galaxy, and gravitational wave kicks as a result of mergers.

@@

The central density, $\rho_c$, can be found from inverting Equation 5 for the galaxy's total mass in Stone-Ostriker:

@@

We also give $r_c$ an initial value of 100 pc, which is reasonable for a cored massive system.  We can then equate the value for $\sigma({R_e})$ obtained from Equation \ref{sig} to the analytic expressions for $\sigma$ in the Stone-Ostriker profile (cf. Eqns 9 and A1-A4).  The only unknown is $r_h$, which we can solve for using a simple recursive Newton method.  Whether $\sigma_{near}$ or $\sigma_{far}$ is used from Stone-Ostriker is determined by whether $R_e$ is less than or greater than $\sqrt{r_c r_h}$.

@@

\subsubsection{Gravitational wave recoils and escape}
The code \textsc{AR-Chain} includes post-Newtonian terms up to order 2.5. The SMBHs can therefore merge via gravitational wave emission. We include gravitational wave recoils following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.  We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than 1.0x the Schwarzschild radius. At the moment of the merger, we also assume that the spin vectors of the two SBHs are randomly aligned.

A result of the anisotropic emission of gravitational waves is that the merged binary often experiences a linear kick in the opposite direction of the emission of the GW due to conservation of linear momentum. This kick can result in velocities of the merged binary from approximately $200-5000\ km s^{-1}$ (see \citealt{2007PhRvL..98w1101G, 2007PhRvL..98i1101G, 2007PhRvL..98w1102C, 2011PhRvL.107w1102L}.  In our simulations, the binaries never stray more than a few tens of parsecs from the nucleus of the host galaxies.

@@

\subsection{Simulation setup}\label{subsec:simset}
For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined from \citet{2008gady.book.....B} as:
\begin{equation}\label{tfric}
    t_{fric} = \frac{19}{6}\left(\frac{R_\mathrm{e}}{5\mathrm{kpc}}\right)^2\frac{\sigma(R_\mathrm{e})}{200\mathrm{km}\,\mathrm{s}^{-1}}\frac{10^8\,M_{\odot}}{M_\mathrm{BH}} \text{  Gyr},
\end{equation}
The orbiting black holes were injected into their host galaxy at redshift z, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.  Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{GM(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.

@@

\subsubsection{Gas Environment Surrounding Black Holes}
In order to model the surrounding environment of the wandering black holes, we used the data and scaling relations from \citet{2018ApJ...857...32B}, which are based on Chandra X-ray observations of 94 early-type, gas poor galaxies of several morphological types (elliptical, lenticular, SB, BCGs, and cD galaxies).  In particular, we used data from Tables 2 and 3 for temperature in X-ray ($T_X$) and central gas density ($\rho_0$) to model the surrounding gas properties.  Central velocity dispersion ($\sigma_c$) was used as the independent variable.  We estimate the central velocity dispersion in this work based on the potential-density profile in  \citet{2015ApJ...806L..28S} that was also used in modeling the potential in the simulations (cf their equation 11):
\begin{equation}
    \sigma^2 = \frac{6GM_{tot}(\frac{\pi^2}{8}-1)}{{\pi}r_h},
\end{equation}
where G is the gravitational constant, $M_{tot}$ is the total galaxy mass (stars + DM), and $r_h$ is the outer halo radius as defined in the Stone-Ostriker profile (cf. equation 1).

Figures \ref{fig:rho0_vs_sigma} and \ref{fig:Tx_vs_sigma} present the data from \citet{2018ApJ...857...32B}, along with the simple linear fits (in log-log space) and resulting gas properties used for our galaxies:
\begin{subequations} \label{eq:gas_properties}
\begin{eqnarray}
    \rho_0 = 10^{0.6*\log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 25} \text{  g cm}^{-3},\\
    T_x = 10^{2.50*\log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 6.06} \text{  keV}.
\end{eqnarray}
\end{subequations}

The dispersion of the data around the fit for $\rho_0$ is at most 1.5-2.0 orders of magnitude.  This leads to a similar variation in the gas density surrounding the black hole, in addition to the ultimate accretion rate of the black hole, due to both having a linear dependence on the central gas density (see Eqns \eqref{beta_model} and \eqref{net_accretion} below).

The dispersion of the X-ray temperature data around the fit is approximately 1-1.5 orders of magnitude.  The gas sound speed (see Equation \eqref{gas_sound_speed} below) has a $C_s{\sim}T_x^{0.5}$ dependence on temperature.  However, given the dependence of the accretion rate (see Equation \eqref{net_accretion} below) on gas sound speed of $\dot{M}_{acc}{\sim}C_s^3$, the accretion rate is dependent on temperature to the order of $T_x^{3/2}$.  This is another source of variation in our estimate of accretion rate.

@@

The sound speed of the gas, $C_s$, is derived from the ideal gas law:
\begin{equation}\label{gas_sound_speed}
    C_s = \sqrt{1.67T_x*\expnumber{1.602}{-16}/m_p} \text{  km s}^{-1},
\end{equation}
where $m_p$ is the proton mass in kilograms.  Since $T_x$ is in keV, the factor of $\expnumber{1.602}{-16}$ is added to convert the temperature to Joules.

The resulting net black hole mass accretion rate is approximated by \citet{1944MNRAS.104..273B} and \citet{1952MNRAS.112..195B}:
\begin{equation}\label{net_accretion}
    \dot{M}_{acc} = f\frac{4{\pi}G^2M_\mathrm{BH}^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
\end{equation}
where the additional factor $f$ (see \cite{2018MNRAS.476.1412I} and \cite{2019MNRAS.486.5377I}) gives the decline in accretion, interior to the BH radius due to convective (i.e., inefficient) accretion, as calculated in \citet{2019MNRAS.486.5377I}, cf. eq 13.  Additionally, $M_{BH}$ is the black hole mass, $G$ is the gravitational constant, and $v$ is the black hole velocity.

Finally, the black hole X-ray luminosity is estimated from:
\begin{equation}
    L_x = \epsilon_{rx}\dot{M}_{acc}c^2 \text{  erg s}^{-1},
\end{equation}
where the X-ray radiative efficiency ${\epsilon}_{rx}=0.01$ , and we are assuming for the low-luminosity sources that $L_x{\sim}L_{Bol}$.  For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$, due to the higher net accretion onto the black hole as a result of cooling of the accretion disc and hence higher gas density.
The corresponding Eddington limit is defined as:
\begin{equation}
    L_{edd} = 1.26 \times 10^{38} (M/M_{\odot}) \text{  erg s}^{-1}.
\end{equation}

@@

\subsubsection{Final X-ray Luminosities of Wandering Black Holes, and Expected Detection Spectra}
Figure \ref{fig:loobhs} is an approximation to Figure 12 from \cite{2019MNRAS.486.5377I}, along with the final $L_{Bol}/L_{Edd}$ ratio of the wandering black holes from this study, although extended below $10^{-6}$ $\dot{M}_{B}/\dot{M}_{Edd}$ for the very low accretion-rate sources.  Indeed, such low luminosity sources are common, with some estimates of $L_{Bol}/L_{Edd}$ as low as $10^{-10}$ ( e.g., \citealt{2003ApJ...598..301Y}, \citealt{2004ApJ...613..322Q}, \citealt{2008ARA&A..46..475H}, \citealt{2009ApJ...699..626H}, \citealt{2018MNRAS.476.1412I}).
\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"luminosities_final".png}
\caption{Approximation to Figure 12 from \citealt{2019MNRAS.486.5377I}. Black "o"s represent black holes in this study.  We also include observational results for Sgr A*, and BHs in M31 and M87.}
\label{fig:loobhs}
\end{center}
\end{figure}

>>>>

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage{comment}

@@

\begin{abstract}
We perform N-body simulations on some of the most massive galaxies extracted from a cosmological simulation of hierarchical structure formation with total masses in the range $10^{12} M_{\sun} < M_{tot} < 3\times 10^{13} M_{\sun}$ from $4\geq z \geq 0$.  After galactic mergers, we track the dynamical evolution of the infalling black holes (BHs) around their host's central BHs.  From 11 different simulations, we find that, of the 86 infalling BHs with masses > $10^4 M_{\sun}$, 36 merge with their host's central BH, 13 are ejected from their host galaxy, and 37 are still orbiting at $z=0$.  Across all galaxies, 33 BHs are kicked to a higher orbit after close interactions with the central BH binary or multiple, after which only one of them merged with their hosts.  These orbiting BHs should be detectable by their anomalous (not Low Mass X-ray Binary) spectra.  The X-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{28}-10^{43}$ $\mathrm{erg}~\mathrm{s}^{-1}$, with a currently undetectable median value of $10^{33}$ $\mathrm{erg}~\mathrm{s}^{-1}$.  However, the most luminous $\sim$5\% should be detectable by existing X-ray facilities.
\end{abstract}

@@

\subsection{Overview of simulation}
The computational challenge of this investigation is a wide range of time-scales. Galactic evolution and galactic orbits take hundreds of millions to billions of years, while orbital times of BH binaries may require time steps of years for accurate integration. We overcome this challenge by simplifying the model where possible, and by focussing on the main drivers of BH dynamics: the galactic background potential, dynamical friction, and strong BH-BH encounters.

@@

For the numerical simulations presented here, we used a modified version of the algorithmic chain integrator \textsc{AR-Chain} developed by \citet{2006MNRAS.372..219M}. It uses algorithmic chain regularization for high-precision integration of few-body dynamics, and is capable of handling velocity-dependent forces efficiently. It includes relativistic post-Newtonian terms up to order 2.5 \citep{2008AJ....135.2398M}.

@@

\citet{2012MNRAS.425..641L}, using \citet{2011ApJ...741...99C}'s work as a basis, created galactic merger trees that compared the properties of in-situ and accreted stellar mass of galaxies at redshift snapshots between $4\geq z \geq0$.

@@

\subsubsection{Stellar Mass Adjustment}
As we will explain further in Section \ref{Galaxy background potential}, in our simulations orbiting black holes are inserted into the host galaxy at the effective radius, $R_e$, which is partially dependent on stellar mass, $M_*$ (see Equation \ref{re}).  For every doubling of the stellar mass, $R_e$ increases by a factor of 1.66.  Additionally, the velocity dispersion at the effective radius, $\sigma(R_e)$, which is used to set the parameter $r_h$ (see Equation \ref{jerry}) of our dark matter profile, is also dependent on $M_*$.  In this case, a doubling of $M_*$ would increase $\sigma(R_e)$ by a factor of 1.15.  These variations have direct effects on the ability of the orbiting black holes to merge with the central black hole, and thus can affect our merger statistics and resulting characteristic strain calculations, and therefore it is important to estimate our stellar masses with reasonable accuracy.

@@

\subsection{Simulation Physics}
In this section, we describe the underlying physics of our simulations, including choice of galaxy background potential, BH diffusion through the galaxy, and gravitational wave kicks as a result of black hole mergers.

@@

The central density, $\rho_c$, can be found from inverting Equation 5 in Stone and Ostriker 2015 for the galaxy's total mass:

@@

We also give $r_c$ an initial value of 100 pc, which is reasonable for a cored massive system.  We can then equate the value for $\sigma({R_e})$ obtained from Equation \ref{sig} to the analytic expressions for $\sigma$ in the Stone-Ostriker profile (cf. Equations 9 and A1-A4).  The only unknown is $r_h$, which we can solve for using a simple recursive Newton method.  Whether $\sigma_{near}$ or $\sigma_{far}$ is used from Stone-Ostriker is determined by whether $R_e$ is less than or greater than $\sqrt{r_c r_h}$.

@@

\subsubsection{Gravitational wave recoils and escape}
The code \textsc{AR-Chain} includes post-Newtonian terms up to order 2.5. The SMBHs can therefore merge via gravitational wave emission. We include gravitational wave recoils following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.  We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than the Schwarzschild radius. At the moment of the merger, we also assume that the spin vectors of the two SBHs are randomly aligned.

A result of the anisotropic emission of gravitational waves is that the merged binary often experiences a linear kick in the opposite direction of the emission of the GW due to conservation of linear momentum. This kick can result in velocities of the merged binary from approximately $200-5000\ km\ s^{-1}$ (see \citealt{2007PhRvL..98w1101G, 2007PhRvL..98i1101G, 2007PhRvL..98w1102C, 2011PhRvL.107w1102L}).  In our simulations, the binaries never stray more than a few tens of parsecs from the nucleus of the host galaxies.

@@

\subsection{Simulation setup}\label{subsec:simset}
For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined from \citet{2008gady.book.....B} as:
\begin{equation}\label{tfric}
    t_{fric} = \frac{19}{6}\left(\frac{R_\mathrm{e}}{5\mathrm{kpc}}\right)^2\frac{\sigma(R_\mathrm{e})}{200\mathrm{km}\,\mathrm{s}^{-1}}\frac{10^8\,M_{\odot}}{M_\mathrm{BH}} \text{  Gyr},
\end{equation}
The orbiting black holes were injected into their host galaxy at redshift $z$, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.  Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{GM(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.

@@

\subsubsection{Gas Environment Surrounding Black Holes}
In order to model the surrounding environment of the wandering black holes, we used the data and scaling relations from \citet{2018ApJ...857...32B}, which are based on Chandra X-ray observations of 94 early-type, gas poor galaxies of several morphological types (elliptical, lenticular, SB, BCGs, and cD galaxies).  In particular, we used data from Tables 2 and 3 for temperature in X-ray ($T_x$) and central gas density ($\rho_0$) to model the surrounding gas properties.  Central velocity dispersion ($\sigma_c$) was used as the independent variable.  We estimate the central velocity dispersion in this work based on the potential-density profile in  \citet{2015ApJ...806L..28S} that was also used in modeling the potential in the simulations (cf their equation 11):
\begin{equation}
    \sigma^2 = \frac{6GM_{tot}(\frac{\pi^2}{8}-1)}{{\pi}r_h},
\end{equation}
where G is the gravitational constant, $M_{tot}$ is the total galaxy mass (stars + DM), and $r_h$ is the outer halo radius as defined in the Stone-Ostriker profile (cf. equation 1).

Figures \ref{fig:rho0_vs_sigma} and \ref{fig:Tx_vs_sigma} present the data from \citet{2018ApJ...857...32B}, along with the simple linear fits (in log-log space) and resulting gas properties used for our galaxies:
\begin{subequations} \label{eq:gas_properties}
\begin{eqnarray}
    \rho_0 = 10^{0.6*\log\left(\frac{\sigma_c}{km\ s^{-1}}\right) - 25} \text{  g cm}^{-3},\\
    T_x = 10^{2.50*\log\left(\frac{\sigma_c}{km\ s^{-1}}\right) - 6.06} \text{  keV}.
\end{eqnarray}
\end{subequations}

The dispersion of the data around the fit for $\rho_0$ is at most 1.5-2.0 orders of magnitude.  This leads to a similar variation in the gas density surrounding the black hole, in addition to the ultimate accretion rate of the black hole, due to both having a linear dependence on the central gas density (see Equations \eqref{beta_model} and \eqref{net_accretion} below).

The dispersion of the X-ray temperature data around the fit is approximately 1-1.5 orders of magnitude.  The gas sound speed (see Equation \eqref{gas_sound_speed} below) has a $C_s{\propto}T_x^{0.5}$ dependence on temperature.  However, given the dependence of the accretion rate (see Equation \eqref{net_accretion} below) on gas sound speed of $\dot{M}_{acc}{\propto}C_s^3$, the accretion rate is dependent on temperature to the order of $T_x^{3/2}$.  This is another source of variation in our estimate of accretion rate.

@@

The sound speed of the gas, $C_s$, is derived from the ideal gas law:
\begin{equation}\label{gas_sound_speed}
    C_s = \sqrt{1.67T_x*1.602\times10^{-16}/m_p} \text{  km s}^{-1},
\end{equation}
where $m_p$ is the proton mass in kilograms.  Since $T_x$ is in keV, the factor of $1.602\times10^{-16}$ is added to convert the temperature to Joules.

\subsubsection{Black Hole Mass Accretion and Luminosity}
In theory, the black hole mass accretion rate is governed by the Bondi-Hoyle formula (\citet{1944MNRAS.104..273B} and \citet{1952MNRAS.112..195B}):
\begin{equation}\label{net_accretion}
    \dot{M}_{B} = f\frac{4{\pi}G^2M_\mathrm{BH}^2\rho}{(C_s^2+v^2)^{3/2}} \text{  g}\text{ s}^{-1},
\end{equation}
where $\rho$ is the density of the surrounding gas, $C_s$ is the gas sound speed, and $v$ is the velocity of the black hole.

However, due to convective (i.e., inefficient) accretion interior to the Bondi radius (see \cite{2018MNRAS.476.1412I} and \cite{2019MNRAS.486.5377I}), the net accretion to the black hole is often substantially lower than the Bondi-Hoyle accretion.  It can be inferred from the fitting relation given in Equation 31 of \cite{2019MNRAS.486.5377I}:
\begin{equation}\label{inayoshi_accretion}
    \frac{\dot{M}_{\bullet}}{\dot{M}_{Edd}} \simeq 1.5\times10^{-6}T_7^{-4/5}\times\left(\frac{\alpha}{0.01}\right)^{0.37}\left(\frac{\dot{m}_B}{10^{-3}}\right)^{3/5}\left(\frac{f_c}{0.1}\right)^{2/5},
\end{equation}
where $\dot{M}_{\bullet}$ is the net accretion to the black hole, $T_7$ is the temperature of the ambient gas in units of $10^7\;K$, $\alpha$ is the strength of viscosity (generally accepted to be 0.01; see \citet{1973A&A....24..337S}, \citet{1991ApJ...376..214B}, \citet{1995ApJ...445..767M}, \citet{1996ApJ...463..656S}, \citet{1998RvMP...70....1B}, \citet{2004PThPS.155..409S}, \cite{2018MNRAS.476.1412I}), and $f_c$ is the conductivity suppression factor (generally accepted to be 0.1; see \citet{2001ApJ...562L.129N}, \citet{2004PhRvL..92d5001M}, and \cite{2019MNRAS.486.5377I}).  The Eddington accretion rate, $\dot{M}_{Edd}$, is calculated from the Eddington luminosity, $L_{Edd}$, as follows:
\begin{subequations}
    \begin{equation}\label{edd_lum}
        L_{Edd} = 1.26\times10^{38}\left(\frac{M_{BH}}{M_{\odot}}\right)\;\text{erg}\;\text{s}^{-1}
    \end{equation}
    \begin{equation}\label{edd_acc}
        \dot{M}_{Edd} = \frac{L_{Edd}}{0.1c^2} \text{  g} \text{ s}^{-1},
    \end{equation}
\end{subequations}
where $c$ is the speed of light.  Finally, we can define $\dot{m}_{B}$ in Equation \ref{inayoshi_accretion} as  $\dot{m}_{B} = \dot{M}_{B}/\dot{M}_{Edd}$.

Given the above, we estimate the bolometric luminosity of the black holes as $L_{Bol} = \epsilon\dot{M}_{\bullet}c^2$, where $\epsilon$ is the radiative efficiency (cf. Equation 13 in \citet{2019MNRAS.486.5377I}).  For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$, due to the higher net accretion onto the black hole as a result of cooling of the accretion disc and hence higher gas density.  For those having $\dot{M}_B/\dot{M}_{Edd} < 10^{-3}$, we take $L_x=L_{Bol}$.

\begin{comment}
The resulting net black hole mass accretion rate is approximated by \citet{1944MNRAS.104..273B} and \citet{1952MNRAS.112..195B}:
\begin{equation}\label{net_accretion}
    \dot{M}_{acc} = f\frac{4{\pi}G^2M_\mathrm{BH}^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
\end{equation}
where the additional factor $f$ (see \cite{2018MNRAS.476.1412I} and \cite{2019MNRAS.486.5377I}) gives the decline in accretion, interior to the BH radius due to convective (i.e., inefficient) accretion, as calculated in \citet{2019MNRAS.486.5377I}, cf. eq 13.  Additionally, $M_{BH}$ is the black hole mass, $G$ is the gravitational constant, and $v$ is the black hole velocity.

Finally, the black hole X-ray luminosity is estimated from:
\begin{equation}
    L_x = \epsilon_{rx}\dot{M}_{acc}c^2 \text{  erg s}^{-1},
\end{equation}
where the X-ray radiative efficiency ${\epsilon}_{rx}=0.01$ , and we are assuming for the low-luminosity sources that $L_x{\sim}L_{Bol}$.  For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$, due to the higher net accretion onto the black hole as a result of cooling of the accretion disc and hence higher gas density.
The corresponding Eddington limit is defined as:
\begin{equation}
    L_{edd} = 1.26 \times 10^{38} (M/M_{\odot}) \text{  erg s}^{-1}.
\end{equation}
\end{comment}

@@

\subsubsection{Final X-ray Luminosities of Wandering Black Holes, and Expected Detection Spectra}
Figure \ref{fig:loobhs} is an approximation to Figure 12 from \cite{2019MNRAS.486.5377I}, along with the final $L_{Bol}/L_{Edd}$ ratio of the wandering black holes from this study, although extended below $10^{-6}$ $\dot{M}_{B}/\dot{M}_{Edd}$ for the very low accretion-rate sources.  Indeed, such low luminosity sources are common, with some estimates of $L_{Bol}/L_{Edd}$ as low as $10^{-10}$ ( e.g., \citealt{2003ApJ...598..301Y}, \citealt{2004ApJ...613..322Q}, \citealt{2008ARA&A..46..475H}, \citealt{2009ApJ...699..626H}, \citealt{2018MNRAS.476.1412I}).
\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"luminosities_final_final".png}
\caption{Approximation to Figure 12 from \citealt{2019MNRAS.486.5377I}. Black "o"s represent black holes in this study.  We also include observational results for Sgr A*, and BHs in M31 and M87.}
\label{fig:loobhs}
\end{center}
\end{figure}
